Global Distribution of Unintended Pregnancies and Contraceptive Usage

### 2024-04-16 products/manuscript/Manuscript.qmd
Project 5 Updates
Figure caption update still looked incorrect when rendered, so I tried again.

After deciding on a single outcome variable, we created a summary table with that outcome and the seven predictors we will use to predict it, which can be seen @table1.
```{r}
#| message: false
#| label: table1
#| tbl-cap: "Table 1: Summary Table Of Numeric Variables"
#| echo: FALSE
predictortable<- readRDS(here("results", "tables", "predictortable.rds"))
predictortable
```

We created a multitude of exploratory plots to understand our data better. The first exploratory result shown in @figure1 displays the distribution of the outcome variable: percent of unintended pregnancies due to short acting reversible methods. The `pct_upreg_sarc` variable is slightly skewed to the right with an average around 12%.
```{r}
#| message: false
#| label: figure1
#| fig-cap: "Plot 1: Histogram Depicting Number of Countries With Percent Unintended Pregnancy Using SARC"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "exploratory-figures", "pctupreg_sarc_distribution.png"))
```

>>>>

After deciding on a single outcome variable, we created a summary table with that outcome and the seven predictors we will use to predict it, which can be seen @table-1.
```{r}
#| message: false
#| label: table-1
#| tbl-cap: "Table 1: Summary Table Of Numeric Variables"
#| echo: FALSE
predictortable<- readRDS(here("results", "tables", "predictortable.rds"))
predictortable
```

We created a multitude of exploratory plots to understand our data better. The first exploratory result shown in @figure-1 displays the distribution of the outcome variable: percent of unintended pregnancies due to short acting reversible methods. The `pct_upreg_sarc` variable is slightly skewed to the right with an average around 12%.
```{r}
#| message: false
#| label: figure-1
#| fig-cap: "Plot 1: Histogram Depicting Number of Countries With Percent Unintended Pregnancy Using SARC"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "exploratory-figures", "pctupreg_sarc_distribution.png"))
```
